A thermodynamic view of dusty protoplanetary disks: axisymmetric stability

### 2016-11-11 summary.tex
notation change for dg vel diff

The one-fluid formulation, 
Eqs. \ref{masseq}---\ref{tempeq}, can 
produce spuriously-growing modes with frequency $|\sigma|\gtrsim
\Omega$ (see Appendix \S\ref{spurious_epi}). This 
results from neglecting terms of $O(|\Delta\bm{v}|^2)$ when converting
the full two-fluid equations to the one-fluid formulation. The full
one-fluid equations 
%is significantly more complex than our 
%model \cite[e.g.][]{laibe14}. It 
 includes an evolutionary equation for $\Delta\bm{v}$, which has no
 hydrodynamic counter-part \citep{laibe14}. However, it is
 still possible to improve upon 
 the first-order formulation whilst retaining similarilty to  
 standard hydrodynamics.  
%without having the complexity of the full equations

The full one-fluid equations of motion includes the acceleration term 
\begin{align}
%\left.\frac{D\bm{v}}{Dt}\right|_\mathrm{add} = 
%\bm{a} =  
-\frac{1}{\rho}\nabla\cdot\left(\frac{\rhod\rhog}{\rho}\Delta\bm{v}\otimes\Delta\bm{v}\right) 
\equiv  \frac{1}{\rho}\nabla\cdot \bm{T} 
\end{align}
\citep{youdin05a}, 
where $\bm{T}$ is an effective stress tensor. 
In the terminal velocity
approximation with $\Delta\bm{v} = \tstop 
\nabla P/\rhog$, we have 
\begin{align}
\bm{T} = - \frac{\epsilon\tstop^2}{\rho}\nabla P \otimes \nabla P.
\end{align}
If we define 
\begin{align}
  \bm{g} \equiv \sqrt{4\pi G \epsilon \rho} \frac{\nabla P}{\rho}
  \tstop,\label{effective_g} 
\end{align}
then
\begin{align}
\bm{T} = - \frac{1}{4\pi G} \bm{g}\otimes\bm{g}, \label{effective_gstress}
\end{align}
%{\bf tensor virial theorems?}
which is just the anisotropic part of the  
gravitational stress tensor in self-gravitating hydrodynamics 
\citep{lynden-bell72}.

>>>>

The one-fluid formulation, 
Eqs. \ref{masseq}---\ref{tempeq}, can 
produce spuriously-growing modes with frequency $|\sigma|\gtrsim
\Omega$ (see Appendix \S\ref{spurious_epi}). This 
results from neglecting terms of $O(|\widetilde{\bm{v}}|^2)$ when converting
the full two-fluid equations to the one-fluid formulation. The full
one-fluid equations 
%is significantly more complex than our 
%model \cite[e.g.][]{laibe14}. It 
 includes an evolutionary equation for $\widetilde{\bm{v}}$, which has no
 hydrodynamic counter-part \citep{laibe14}. However, it is
 still possible to improve upon 
 the first-order formulation whilst retaining similarilty to  
 standard hydrodynamics.  
%without having the complexity of the full equations

The full one-fluid equations of motion includes the acceleration term 
\begin{align}
%\left.\frac{D\bm{v}}{Dt}\right|_\mathrm{add} = 
%\bm{a} =  
-\frac{1}{\rho}\nabla\cdot\left(\frac{\rhod\rhog}{\rho}\widetilde{\bm{v}}\otimes\widetilde{\bm{v}}\right) 
\equiv  \frac{1}{\rho}\nabla\cdot \bm{T} 
\end{align}
\citep{youdin05a}, 
where $\bm{T}$ is an effective stress tensor. 
In the terminal velocity
approximation with $\widetilde{\bm{v}} = \tstop 
\nabla P/\rhog$, we have 
\begin{align}
\bm{T} = - \frac{\epsilon\tstop^2}{\rho}\nabla P \otimes \nabla P.
\end{align}
If we define 
\begin{align}
  \bm{g} \equiv \sqrt{4\pi G \epsilon \rho} \frac{\nabla P}{\rho}
  \tstop,\label{effective_g} 
\end{align}
then
\begin{align}
\bm{T} = - \frac{1}{4\pi G} \bm{g}\otimes\bm{g}, \label{effective_gstress}
\end{align}
%{\bf tensor virial theorems?}
which is just the anisotropic part of the  
gravitational stress tensor in self-gravitating hydrodynamics 
\citep{lynden-bell72}.
